Psychological Needs During Intergroup Contact

### 2021-10-06 PreregistrationAOT-M.Rmd
typos

1. Entry Survey: A pre-measurement questionnaire (appr. 25 minutes) including demographic information, and relations to the Dutch majority. (payment: 2 Euros)
2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day. (payment: 1 Euro per Recap; up to 2 Euros per day)
3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflection of the study. (payment: 2 Euros)

After the initial 30 day duration, participants are offered the possibility to continue participating in the study either with payment if daily diary measures were missed during the initial study phase or without payment after a total of 60 daily diary measurements were completed. After the initial 30-day period, participants receive automated feedback based on their own well-being, attitudes, and motive responses as an additional initiative give participants access to their own data and to compensate study participation.

@@

Our target sample size is a sum of 4,000 daily diary measurements. With 100% completion rate that would be archieved with 67 participants (60 daily diary responses each). Given that we expect some incomplete daily diary measurements, we aimed to recruit 80 participants.

@@

The targeted sample size depended on a combination of different factors. Different analyses were planned as part of the collaboration and budgeting was a practical constraint. Some analyses were planned based on (1) the pre- to post measurements, (2) the dynamic developments over the daily diary measurements, as well (3) the contemporary effects within the daily diary measurements.

@@

Given the (unexpectedly) large sample size of contemporaneous measurements, we will remove all instances during which a participant did not respond to any of the relevant variables.

>>>>

1. Entry Survey: A pre-measurement questionnaire (appr. 25 minutes) including demographic information, and relations to the Dutch majority. (payment: 2 Euros)
2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day. (payment: 1 Euro per Recap; up to 2 Euros per day)
3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflections on the study. (payment: 2 Euros)

After the initial 30 day duration, participants are offered the possibility to continue participating in the study either with payment if daily diary measures were missed during the initial study phase or without payment after a total of 60 daily diary measurements were completed. After the initial 30-day period, participants receive automated feedback visualizing the development of their own well-being, attitudes, and motive responses as an additional initiative to give participants access to their own data and to compensate study participation.

@@

Our target sample size is a sum of 4,000 daily diary measurements. With 100% completion rate that would be archived with 67 participants (60 daily diary responses each). Given that we expect some incomplete daily diary measurements, we aimed to recruit 80 participants.

@@

The targeted sample size depended on a combination of different factors. Different analyses were planned as part of the collaboration and budgeting was a practical constraint. Some analyses were planned based on (1) the pre- to post measurements, (2) the dynamic developments over the daily diary measurements, or (3) the contemporary effects within the daily diary measurements.

@@

Given the (expectedly) large sample size of contemporaneous measurements, we will remove all instances during which a participant did not respond to any of the relevant variables.
